### 2016-04-06 lineups.Rnw
add new code and rnw files

\newcommand{\hh}[1]{{\color{magenta} #1}}

@@

\hh{Could you crop the white space from the lineup before saving it? - maybe this blog post helps: {http://robjhyndman.com/hyndsight/crop-r-figures/}}

\hh{Please add frames around the panels - it helps with separating the graphs from one another}

>>>>

\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\st}[1]{{\color{purple} #1}}

@@

\hh{Could you crop the white space from the lineup before saving it? - maybe this blog post helps: {http://robjhyndman.com/hyndsight/crop-r-figures/}} \st{I cropped them using pdfcrop for now. I'll add the rest to the function.}

\hh{Please add frames around the panels - it helps with separating the graphs from one another} \st{Okay - easy fix!}
